Holomorphic field theories and higher algebra

### 2022-11-17 draft.tex
odds and ends

\owen{Much of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}

\owen{We can cut this sharply now. My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}

@@

@@

@@

The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle $\mathrm{ad}(\cP) \to X$.
The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}

@@

A twisted matter multiplet also defines a field theory on any complex surface $X$. 
\owen{Is it a cotangent theory? It looks like a twisted cotangent theory.}
\brian{right, $i_{dW}$ is the `twist'.}
The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$ \brian{How do you feel about the notation $\RR \text{Crit}(W)$?}, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
(It is the Koszul complex associated to the Jacobi ring of $W$.)
This description makes manifest an odd symplectic structure on ${\rm Crit}^d(W)$,
as polyvector fields are an odd Poisson algebra via the Schouten bracket.
%As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.\footnote{Notice that AKSZ formalism equips this mapping space with a $1$-shifted symplectic structure as opposed to the desired $(-1)$-shifted symplectic structure.
Hereon we totalize all gradings to $\ZZ/2$.}

Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
\owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
\owen{Part of my concern is that Hamiltonian reduction is a version of GIT, and hence it is {\em not} stacky. The stack quotient seems more appropriate to me.}
%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
\]
which comes equipped with an odd symplectic structure. 
\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
\brian{That's already in this hamiltonian reduction. 
If $V$ is $(-1)$ shifted symplectic then I think the tangent space of $V \Sslash G$ should be
\beqn
\lie{g}[1] \oplus V \oplus \lie{g}^*[-2] .
\eeqn
Since we're forgetting to $\ZZ/2$ this is just $\Pi \lie{g} \oplus (V \oplus \lie{g})$.
}

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $\underline{N} = \CC^N$ with its natural left action.
\owen{That's kind of crappy notation. Let's discuss.}

@@

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
%We will denote this theory by $\cT(N,F)$.
\end{dfn}

>>>>

\owen{Some of what's below is borrowed and scarcely modified from the books, so we probably should do more revision so it's not plagiarism!}

\owen{My main concerns are (1) to mention working on arbitrary complex manifolds and not just $\CC^d$, (2) to mention Beilinson-Drinfeld's approach, and (3) to explain chiralization/reduction for $d > 1$.}

@@

\begin{rmk}
The reader fond of higher abstract nonsense will note that we could have factorization algebras take values in other target categories (better, $\infty$-categories),
not just vector spaces or cochain complexes.
For instance, one might assign an $\infty$-category to each open set.
This generalization is fruitful.
In the Beilinson-Drinfeld style, it leads to chiral categories, which play an increasingly central role in the geometric Langlands program.
In the style advocated above, it would likewise be useful for capturing notions like defects or extended operators from quantum field theory.
\end{rmk}

@@

\owen{Somewhere we should mention Henriques' work connecting factorization algebras with conformal nets,
Daniel Bruegmann's thesis, and how the web of 2d CFT stuff should fit together.}

@@

The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle $\mathrm{ad}(\cP) \to X$.
The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
(Note that $T^*[1]BG_{\CC}$ is the coadjoint quotient stack $[\fg_\CC^*/G_{\CC}]$.)

@@

A twisted matter multiplet also defines a field theory on any complex surface $X$. 
The superpotential determines a derived affine scheme: the derived critical locus ${\rm Crit}^d(W)$, which can be modeled as the spectrum of the dg algebra given by polyvector fields $PV(V)$ on $V$ with differential $\iota_{\d W}$.
(It is the Koszul complex associated to the Jacobi ring of $W$.)
This description makes manifest an odd symplectic structure on ${\rm Crit}^d(W)$,
as polyvector fields are an odd Poisson algebra via the Schouten bracket.
%As a dg space, the ring of functions of the derived critical locus is $\cO(\T^* [-1] V)$ equipped with the differential $\iota_{\d W}$. 
By itself (i.e., before coupling to a gauge theory) the twisted matter multiplet corresponds to the mapping space ${\rm Map}(X, {\rm Crit}^d(W))$.\footnote{Notice that AKSZ formalism equips this mapping space with a $1$-shifted symplectic structure as opposed to the desired $(-1)$-shifted symplectic structure.
Hereon we totalize all gradings to $\ZZ/2$.}

The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , \left( \fg_\CC^*\times {\rm Crit}^d(W) \right)/ G_\CC), 
\]
where the target is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $\underline{N} = \CC^N$ with its natural left action.

@@

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
%We will denote this theory by $\cT(N,F)$.
\end{dfn}
